Transformations of forecasts for evaluation in an epidemiological context

### 2022-11-29 main.tex
add abstract and authors, update paper after feedback

\title{To log or not to log}
  \author{Anonymous Alpaca\thanks{All Alpaca friends} $^{,}$\thanks{The Zoo} $^{ , *}$}

\maketitle

%\tableofcontents

\begin{abstract}
In the abstract, this article is a very good one. We did a very good job of the research and got all the best results. People told us we were mad and we said no we are effective. Now gather around and listen to our thoughts you will be, shocked, scared, amazed, and astounded.
\end{abstract}

@@

{\footnotesize $^*$ Correspondence to: Anonymous Alpaca (\url{anonymous@alpaca.com}))}

@@

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Forecasters, in expectation, optimise their score by providing a predictive distribution that is equal to the data-generating distribution, and are penalised if they fail to do so. 
Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funk19_assessingperformancereal}}, and the Weighted Interval Score \citep[WIS,][formulas given in Section \ref{wis} in the SI]{bracherEvaluatingEpidemicForecasts2021} for predictive distributions represented by a set of predictive quantiles, used to assess forecasts in COVID-19 forecast hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS and the (C)RPS measure the absolute distance between the predictive distribution and the observed value and can be understood as a generalisation of the absolute error to full predictive distributions (see details in Sections \ref{wis} and \ref{crps} in the SI). For simplicity, we will use "absolute error" and "absolute distance" interchangeably, even though the former applies only to point forecasts and the latter is more appropriate for predictive distributions.

Infectious processes are commonly modelled around the concept of the reproduction number, the average number of new cases generated by each case in the population.
In the absence of changes in immunity, behaviour or other factors that may affect the intensity of transmission, the reproduction number would be expected to remain approximately constant.
In that case, the number of new infections in the population grows exponentially in time~\citep{dushoff2021_speedstrengthepidemic}.
This behaviour was observed, for example, early in the COVID-19 pandemic in many countries~\citep{pellis21_challengescontrolcovid}.
If case numbers are changing exponentially and the true modelling task revolves around estimating the reproduction number or the corresponding growth rate, evaluating forecasts based on the absolute distance between forecast and observed value rewards underprediction compared to overprediction by the same amount, as these errors grow exponentially with the error on the estimated reproduction number or growth rate.
Instead, if one is to assess the ability of forecasts to assess and forecast the underlying infection dynamics, it may be more appropriate to evaluate errors on the growth rate directly.

Moreover, if forecasts based are evaluated on absolute rather than relative errors whereas in reality errors scale with the level of observations, scores are strongly influenced by the overall order of magnitude of the quantity to forecast.
This makes it difficult compare predictive performance across time or to compare performance across targets that generally occur different orders of magnitudes.
In the example of COVID-19 where case numbers underwent drastic changes over time following the initial emergence, forecast evaluation based on the absolute numbers would be dominated by performance around the peaks, and evaluation based on jointly evaluating the ability to predict numbers of cases, hospitalisation and deaths dominated by cases as they occur at largest numbers.

In this paper, we discuss how log-transforming the forecasts and observations prior to applying the WIS (or CRPS) may be an appropriate way to address the aforementioned issues with evaluating forecasts based on absolute errors. We first outline the motivation for transforming forecasts prior to scoring (section [REF]). We then provide a mathematical intuition of the impact of scoring on the log scale and its interpretation (section [REF]). We illustrate our findings on a series of examples using forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. Finally, we give scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues on the use of transformed scores in the evaluation of infectious disease forecasts.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{log-transforming forecasts and observations}

Our aim in log-transforming forecasts and observations is to shift the focus of the evaluation in a way that may more appropriate for epidemiological forecasts, while preserving the propriety of the score. Instead of a score representing the magnitude of absolute errors this approach makes it possible to obtain a score which a) measures relative error and at the same time b) provides an approximate measure for how well a forecast captures the multiplicative growth rate of the target quantity. Focusing on relative errors mitigates issues with scores based on absolute errors that are heavily influenced by the order of magnitude of the quantity to forecast. The interpretation of the log-transformed score as an approximate score for a forecast of the growth rate of a given quantity aligns the evaluation with our understanding of how epidemiological processes should be modeled and the kinds of errors models would typically make [CITATION?]. In this paper we focus on the log-transformation, but note that many other transformations may be useful and appropriate (see section \ref{sec:discussion}).
We further focus on the WIS as evaluation metric, given its widespread use throughout the COVID-19 pandemic.

\subsection{Interpretation as a score based on multiplicative (relative) errors}

@@

The analogy between the WIS on the log scale and the absolute error of a point forecast on the log scale is slightly inaccurate: While the absolute error on the log scale is exactly symmetric (e.g., predicting 2 instead of 1 would give the same relative error as predicting 0.5), this is not entirely true for the WIS, which is computed for a set of prediction intervals. Due to the fact that upper and lower bounds of individual prediction intervals are affected slightly differently by the log-transformations, small deviations may occur (compare e.g. in Figure \ref{fig:change-in-scores}D the small difference between scores for an observed outcome of $\frac{1}{5}$ and 5).

@@

\subsection{Interpretation as an approximate score of the growth rate}

Computing a score based on the logarithm of the forecast and the observation is also approximately equivalent to scoring a forecast of a multiplicative growth rate of the forecast target, which approximates the more commonly used exponential growth rate. The multiplicative growth rate is defined as
%
\begin{equation}
    g_{t, t+1} = \frac{y_{t+1} - y_t}{y_t},
\end{equation}
%
where $y_{t+1}$ is the forecast target (e.g. reported cases of COVID-19) in the future, $y_t$ is the last known observation and $g_{t, t+1}$ is the growth rate between now ($t$) and $t+1$. 
Using the growth rate, we can express the value of the forecast target in the future as such: 
%
\begin{equation}
y_{t+1} = (1 + g_{t, t+1}) \cdot y_t.
\end{equation}
%

Now consider a forecast of $\log y_{t+1}$, where again, the score is determined by the size of $\varepsilon^*_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \nonumber\\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon^*_{t+1} \Leftrightarrow \nonumber \\
\nonumber \\
\varepsilon^*_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \nonumber \\    
                    &= \log \left(\frac{y_{t+1}}{y_t}\right) - \log (1 + \hat{g}_{t, t+1}) \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1})\nonumber  \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small differences between } \hat{g}_{t, t+1} \text{ and } g_{t, t+1}. \nonumber
\end{align}

@@

\subsection{Effects on model rankings}
Rankings between different forecasters may change through the log-transformation both when looking at aggregate scores as well as when looking at a single forecast. As an example for the effect on a single forecast, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would equal the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.6}{0.9}) = 1.06$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of her prediction interval, while only being slightly further away with the upper interval. This implies that scores on the log scale may treat (one-sided) outlier forecasts more leniently.

% PARAGRAPH NEEDS SOME WORK
Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is not mainly driven by the kinds of changes in model rankings for single forecasts just discussed. Rather, as observations from exponential processes are likely to be on very different absolute scales, large observations will account for the majority of absolute score but will not dominate relative scores in the same way. When aggregating scores across metrics with different scales, for example reported cases, and hospitalisations, even an ideal (i.e. perfect) forecaster will make much larger errors when predicting case numbers than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log-transforming forecasts and observations may also result in the opposite extreme because small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This can be exacerbated when forecasts are restricted to discrete values, where relative steps between possible values become greater closer to zero.

@@

Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest. For simulated count data following a negative binomial distribution, for example, log predictions for small quantities receive on average higher scores than forecasts for large quantities if the mean and the variance grow at the same rate $\sigma^2 = \mu$, about equal scores when the variance grows at a rate of $\sigma^2 = \mu + \mu^2$ (Figure \ref{fig:SIM-wis-state-size-mean}), and smaller scores when the variance grows faster than that. 
% To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

\subsection{Practical considerations}

The log-transformation is permissible (in the sense that it preserves propriety of the score), because it is a strictly monotonic transformation. Even though actual rankings between models may change, forecasters will  still minimise her score if they report a predictive distribution that is equal to the data-generating distribution. The order of the operations matters, and applying the log-transformation after scores have been computed, i.e. computing $\log S(F, y)$ results in an improper score. This is because taking the logarithm of the WIS / CRPS results in a score that does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/example-log-first.png}
    \caption{Scores for different forecasts evaluated the WIS and the log WIS. We simulated 1000 observations $Y_i = {\rm e}^{x_i}$, with $x_i \text{iid} \sim \mathcal{N}(0, 1)$. We then simulated 20 forecasters who would issue a predictive distribution $F = {\rm e}^{x_i}$, with $x \sim \mathcal{N}(0, \sigma)$, with values of $\sigma$ ranging from 0.1 to 2.}
    \label{fig:log-improper}
\end{figure}

In practice, one issue with the log-transformation is that it cannot readily be applied to negative numbers or zero values. In addition, it may difficult to reliably evaluate relative errors when dealing with small discrete values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. One solution to deal with zeroes and small values is to also exclude those from ongoing analysis. An alternative is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm as is common practice when log-transforming counts. This represents a strictly monotonic transformation and therefore preserves propriety of the resulting score. The choice of the number to add influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. Adding something to the forecasts and observations changes scores for forecasts of small quantities most, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities.

\section{Empirical example: the European Forecast Hub}

As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. 
The European COVID-19 Forecast Hub is one of several COVID-19 Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021} that systematically collects, aggregates and evaluates forecasts of several COVID-19 targets created by different teams every week. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$).

 2021 and October 18 2021 for reported cases and deaths from COVID-19. We filtered all forecasts submitted to the Hub to only include models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 16 forecast dates (see Figure \ref{fig:HUB-num-avail-models}. Where not otherwise stated, we report results for a two-week-ahead forecast horizon.

In addition to the WIS we use pairwise comparisons \citep{cramerEvaluationIndividualEnsemble2021} to evaluate the relative performance of models across countries in the presence of missingness. In a first step, score ratios are computed for all pairs of models by taking the set of overlapping forecasts between the two models and dividing the score of one model over the score achieved by the other model. The relative skill for a given model is then obtained by taking the geometric mean of all score ratios which involve that model. Low values are better, and the average model receives a relative skill score of 1.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-mean-obs-location.png}
    \caption{Observations and scores across locations and forecast horizons. A, Average (across all time points) of observed cases and deaths for different locations. B: Boxplot (y-axis on log-scale) of all cases and deaths. C: Scores for two-week-ahead forecasts from the EuroCOVIDhub-ensemble (averaged across all forecast dates) for different locations, evaluated on the natural as well as the logarithmic scale. D: Corresponding box-plots of all individual scores for two-week-ahead predictions. E: Boxplots for the relative change of scores for the EuroCOVIDhub-ensemble across forecast horizons. For any given forecast date and location, forecasts were made for four different forecast horizons, resulting in four scores. All scores were divided by the score for forecast horizon one.}
    \label{fig:HUB-mean-locations}
\end{figure}

>>>>

\title{Transformations of forecasts for evaluation in an epidemiological context}
  \author{Nikos I. Bosse\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene & Tropical Medicine, London, United Kingdom} $^{,}$\thanks{Centre for the Mathematical Modelling of Infectious Diseases, London, United Kingdom} $^{,*}$,

  Sam Abbott\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$,

  Anne Cori\thanks{MRC Centre for Outbreak Analysis and Modelling, Department of Infectious Disease Epidemiology, School of Public Health, Imperial College London, London, United Kingdom} $^{}$, \\

  Edwin van Leeuwen\thanks{Department of Infectious Disease Epidemiology, London School of Hygiene & Tropical Medicine, London, United Kingdom} $^{,}$\thanks{UK Health Security Agency, London, United Kingdom} $^{}$,

  Johannes Bracher\thanks{Institute of Economic Theory and Statistics, Karlsruhe Institute of Technology, Karlsruhe, Germany} $^{}$,

  Sebastian Funk\footnotemark[1] $^{,}$\footnotemark[2]$ ^{}$
  }

\maketitle
%\tableofcontents
\begin{abstract}
Forecast evaluation plays an essential role in improving forecasting models can help inform future decision making. In epidemiology, forecasts are often scored using the Weighted Interval Score (WIS) or the Continuous Ranked Probability Score (CRPS), which are a measure of absolute distance between forecast and observation. Infectious disease processes are commonly described in terms of the growth rate or the effective reproduction number. Scoring based on the absolute distance between forecast and observation may not reflect the true underlying modelling task well (estimating the growth rate or reproduction number) and makes it difficult to compare forecasts across time, space, and different targets. As a solution we propose transforming the data before scoring the forecasts. Depending on the context, many transformations may be appropriate. We describe the log-transformation as one specific example in detail and discuss its interpretation as a measure of relative error and an approximate score for a forecast of the growth rate. Applying the log-transformation to data from the European COVID-19 Forecast Hub, we found that it changed model rankings, evened scores across time, locations and target types, and emphasised situations in which models missed lower inflection points and consequent rises in numbers, while penalising missed peaks less severely. 
\end{abstract}

@@

{\footnotesize $^*$ Correspondence to \url{nikos.bosse@lshtm.ac.uk})}

@@

Probabilistic forecasts are usually evaluated using so-called proper scoring rules \citep{gneitingStrictlyProperScoring2007}, which return a numerical score as a function of the forecast and the observed data. Proper scoring rules are constructed such that forecasters are incentivised to report their true belief about the future. Examples of proper scoring rules that have been used to assess epidemiological forecasts are the Continuous Ranked Probability Score~\citep[CRPS,][]{gneitingStrictlyProperScoring2007} or its discrete equivalent, the Ranked Probability Score~\citep[RPS,][]{funk19_assessingperformancereal}, and the Weighted Interval Score \citep[WIS,][formulas given in Section \ref{wis} in the SI]{bracherEvaluatingEpidemicForecasts2021}. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in COVID-19 forecast hubs in the US \citep{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \citep{sherrattPredictivePerformanceMultimodel2022}, Germany and Poland \citep{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US Influenza Forecasting Hub \citep{CdcepiFlusightforecastdata2022}. The WIS and the CRPS measure the absolute distance between the predictive distribution and the observed value and can be understood as a generalisation of the absolute error to predictive distributions (see details in Sections \ref{wis} and \ref{crps} in the SI). For simplicity, we will use "absolute error" and "absolute distance" interchangeably, even though the former is more commonly used for point forecasts and the latter is more appropriate for predictive distributions.

Infectious processes are commonly modelled around the concept of the reproduction number \citep{gosticPracticalConsiderationsMeasuring2020}, the average number of new cases generated by each case in the population.
In the absence of changes in immunity, behaviour or other factors that may affect the intensity of transmission, the reproduction number would be expected to remain approximately constant.
In that case, the number of new infections in the population grows exponentially in time~\citep{dushoff2021_speedstrengthepidemic}.
This behaviour was observed, for example, early in the COVID-19 pandemic in many countries~\citep{pellis21_challengescontrolcovid}.
If case numbers are growing exponentially (for an effective reproduction number greater than 1) and the true modelling task revolves around estimating the reproduction number or the corresponding growth rate, evaluating forecasts based on the absolute distance between forecast and observed value penalises underprediction (of the reproduction number) less than overprediction by the same amount, as errors on the observed value grow exponentially with the error on the estimated reproduction number or growth rate.
If one is to assess the ability of forecasts to assess and forecast the underlying infection dynamics, it may be more appropriate to evaluate errors on the growth rate directly.

Moreover, if forecasts are evaluated based on absolute rather than relative errors, whereas in reality errors scale with the level of observations, scores are strongly influenced by the overall order of magnitude of the quantity to forecast.
This makes it difficult to compare predictive performance across time or to compare performance across targets that generally occur at different orders of magnitudes.
In the example of COVID-19 where case numbers underwent drastic changes over time following the initial emergence, forecast evaluation based on the absolute numbers would be dominated by performance around the peaks, and evaluation based on jointly evaluating the ability to predict numbers of cases, hospitalisation and deaths dominated by cases as they occur at largest numbers.

In this paper, we discuss how transforming the forecasts and observations prior to applying the WIS (or CRPS) may be an appropriate way to address the aforementioned issues. Many different transformations may be appropriate and useful, depending on the exact context, the desired focus of the evaluation, and specific aspects of the forecasts that forecast consumers care most about (see a broader discussion in Section \ref{sec:discussion}). For conceptual clarity and to allow for a more in-depth discussion, we focus most of our attention on the log-transformation as one example of many possible transformations, chosen for its simplicity and usefulness in an epidemiological context. We further focus on the WIS as evaluation metric, given its widespread use throughout the COVID-19 pandemic.

We first outline the motivation for transforming forecasts prior to scoring and specifically the motivation for applying a log-transformation (Section \ref{sec:methods}). We provide a mathematical intuition of the impact of the log-transformation, its interpretation (Section \ref{sec:methods:relative} and \ref{sec:methods:growthrate}) and effects on forecast rankings (section \ref{sec:methods:rankings} and provide some discuss some practical considerations relevant for applying transformations in general and the log-transformation in particular (Section \ref{sec:methods:considerations}). We illustrate our the effect of the log-transformation using forecasts submitted to the European COVID-19 Forecast Hub  \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022} (Section \ref{sec:results}). Finally, we provide scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues on the use of transformed scores in the evaluation of infectious disease forecasts (Section \ref{sec:discussion}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Transforming forecasts and observations}
\label{sec:methods}

Our aim in transforming forecasts and observations is to shift the focus of the evaluation in a way that may be more appropriate for epidemiological forecasts, while preserving the propriety of the score.  Instead of a score representing the magnitude of absolute errors this approach makes it possible to obtain a score which a) measures relative error and at the same time b) provides an approximate measure for how well a forecast captures the multiplicative growth rate of the target quantity (see Section \ref{sec:methods:growthrate}. The interpretation of the log-transformed score as an approximate score for a forecast of the growth rate of a given quantity aligns the evaluation with our understanding of how epidemiological processes should be modeled and the kinds of errors models would typically make.

\subsection{Interpretation as a score based on multiplicative (relative) errors}
\label{sec:methods:relative}

@@

The analogy between the WIS on the log scale and the absolute error of a point forecast on the log scale is slightly inaccurate: while the absolute error on the log scale is exactly symmetric (e.g., predicting 2 instead of 1 would give the same relative error as predicting 0.5), this is not entirely true for the WIS, which is computed for a set of prediction intervals. Due to the fact that upper and lower bounds of individual prediction intervals are affected slightly differently by the log-transformations, small deviations may occur (compare e.g. in Figure \ref{fig:change-in-scores}D the small difference between scores for an observed outcome of $\frac{1}{5}$ and 5).

@@

\subsection{Interpretation as an approximate score of the growth rate}
\label{sec:methods:growthrate}

Computing a score based on the logarithm of the forecast and the observation is also approximately equivalent to scoring a forecast of a multiplicative growth rate of the forecast target, which approximates the more commonly used exponential growth rate. The multiplicative growth rate can be defined as
%
\begin{equation}
    g_{t, t+1} = \frac{y_{t+1} - y_t}{y_t},
\end{equation}
%
where $y_{t+1}$ is the forecast target (e.g. reported cases of COVID-19) in the future, $y_t$ is the last known observation and $g_{t, t+1}$ is the growth rate between now ($t$) and $t+1$. 
Using the growth rate, we can express the value of the forecast target in the future as such: 
%
\begin{equation}
y_{t+1} = (1 + g_{t, t+1}) \cdot y_t.
\end{equation}
%

Now consider a forecast of $\log y_{t+1}$, where again, the score is determined by the size of $\varepsilon^*_{t+1}$. Using the fact that for small values of $x$, $\log (1+ x) \approx x$, we can see that scoring forecasts on the log scale is approximately equal to scoring an additive error on the growth rate (on the natural scale), as long as the growth rate is small.
%
\begin{align}
\log y_{t+1}        &= \log \hat{y}_{t+1} + \varepsilon^*_{t+1} \nonumber\\
                    &= \log ((1 + \hat{g}_{t+1}) \cdot y_{t}) + \varepsilon^*_{t+1} \\
                    &= \log (1 + \hat{g}_{t, t+1}) + \log y_t + \varepsilon^*_{t+1} \Leftrightarrow \nonumber \\
\nonumber \\
\varepsilon^*_{t+1}  &= \log y_{t+1} -  \log y_t - \log (1 + \hat{g}_{t, t+1}) \nonumber \\    
                    &= \log \left(\frac{y_{t+1}}{y_t}\right) - \log (1 + \hat{g}_{t, t+1}) \\    
                    &= \log (1 + g_{t, t+1}) - \log (1 + \hat{g}_{t, t+1})\nonumber  \\   
                    &\approx g_{t, t+1} - \hat{g}_{t, t+1} \quad \text{for small } \hat{g}_{t, t+1} \text{ and } g_{t, t+1}. \nonumber
\end{align}

@@

\subsection{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on their scores may change through the log-transformation both when looking at aggregate scores as well as when looking at a single forecast. As an example for the effect on a single forecast, consider two forecasters, A and B. Both issue a single 50\%-prediction interval for a target which later resolves as 1. Forecaster A issues the interval [0.5, 2], while forecaster B issues [0.9. 2.5]. On the natural scale, the score would equal the dispersion of the forecast, i.e. the length of this interval (since the observed value falls within the prediction interval). Forecaster A would receive a score of $2 - 0.5$ = 1.5, beating forecaster B who would receive a score of $2.5 - 0.9 = 1.6$. When we transform the forecast, forecaster A receives a score of $\log (\frac{2}{0.5}) = 1.39$, while forecaster B obtains a score of $\log (\frac{2.5}{0.9}) = 1.02$ and now wins over forecaster A. The main difference between forecaster A and B is that forecaster A has issued a prediction interval ([0.5, 2]) that was more symmetric around the true value than the interval issued by forecaster B ([0.9. 2.6], which was more skewed). This means that in relative terms, Forecaster B was noticeably closer to the true value with the lower bound of their prediction interval, while only being slightly further away with the upper interval. This implies that scores on the log scale may treat (one-sided) outlier forecasts more leniently.

% PARAGRAPH NEEDS SOME WORK
Overall model rankings would be expected to differ even more when scores are averaged across multiple forecasts or targets. The change in rankings of aggregate scores is not mainly driven by the kinds of changes in model rankings for single forecasts just discussed. Rather, as observations from exponential processes are likely to be on very different absolute scales, large observations will account for the majority of absolute score but will not dominate relative scores in the same way. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log-transforming forecasts and observations may also result in the opposite extreme because small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This can be exacerbated when forecasts are restricted to discrete values, where relative steps between possible values become greater for values closer to zero.

@@

Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest. To provide a better intuition, we simulated count data following a negative binomial distribution. For these simulated data, log predictions for small quantities received on average higher scores than forecasts for large quantities if the mean and the variance grew at the same rate $\sigma^2 = \mu$, about equal scores when the variance grew at a rate of $\sigma^2 = \mu + \mu^2$, and smaller scores when the variance grew faster than that (Figure \ref{fig:SIM-wis-state-size-mean}). 
% To illustrate this with count data we sampled forecasts from different negative binomial distributions. The negative binomial distribution has mean $\mu$ and variance $\sigma^2 = \mu + \mu ^2 / \theta$ and for $\lim_{\theta \to \infty}$ converges to the Poisson distribution. For large values of $\theta$, resulting in a variance approximately equal to the mean, forecasts for lower quantities on average received higher scores on the log scale (see Figure \ref{fig:SIM-wis-state-size-mean}. For $\theta = 1$ (and correspondingly, $\sigma^2 = \mu + \mu^2$, we found that scores on the log scale remained approximately constant regardless of the size of the quantity to forecast. For $\theta = 0.1$ (and $\sigma^2 = \mu + 10 \cdot \mu^2$), scores on the log scale increased with the quantity to forecast. When scored on the natural scale, a higher quantity to forecast always lead to higher scores regardless of the chosen distribution (as long as the variance grows together with the mean).

\subsection{Practical considerations}
\label{sec:methods:considerations}

The log-transformation (among many other transformations) is permissible (in the sense that it preserves propriety of the score), because it is a strictly monotonic transformation. Even though actual rankings between models may change, forecasters will in expectation still minimise their score if they report a predictive distribution that is equal to the data-generating distribution. The order of the operations matters, and applying a transformation after scores have been computed generally does not guarantee propriety. In the specific example, taking the logarithm of the scores, rather than scoring the log-transformed forecasts and data, results in an improper score. This is because taking the logarithm of the WIS / CRPS results in a score that does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/example-log-first.png}
    \caption{Scores for different forecasts evaluated using the WIS and the log WIS. We simulated 1000 observations $Y_i = {\rm e}^{x_i}$, with $x_i \text{ iid} \sim \mathcal{N}(0, 1)$. We then simulated 20 forecasters who would issue a predictive distribution $F = {\rm e}^{x_i}$, with $x \sim \mathcal{N}(0, \sigma)$, with values of $\sigma$ ranging from 0.1 to 2.}
    \label{fig:log-improper}
\end{figure}

In practice, one issue with the log-transformation is that it cannot readily be applied to negative numbers or zero values. In addition, it may be difficult to reliably evaluate relative errors when dealing with small discrete values. In an epidemiological setting that involves count data, negative values should likely be omitted entirely. One solution to deal with zeroes and small values is to also exclude those from ongoing analysis. An alternative is to add a small quantity, such as 1, to all observations and predictions before taking the logarithm as is common practice when log-transforming counts. This represents a strictly monotonic transformation and therefore preserves propriety of the resulting score. The choice of the number to add influences scores and rankings, as measures of relative errors shrink when adding a constant to the forecast and the observation. Adding something to the forecasts and observations changes scores for forecasts of small quantities most, as relative errors shrink more the smaller the original value before adding a constant. In principle, it would also be possible to exploit the difference in how scores are affected in order to equalise scores for forecasts of quantities across different scales by adding a larger number (e.g. 100 or 10,000) if average scores are dominated too strongly by forecasts for small quantities.

\section{Empirical example: the European Forecast Hub}
\label{sec:results}

As an empirical example for evaluating forecasts on the natural and on the log scale we use forecasts from the European Forecast Hub \citep{europeancovid-19forecasthubEuropeanCovid19Forecast2021, sherrattPredictivePerformanceMultimodel2022}. 
The European COVID-19 Forecast Hub is one of several COVID-19 Forecast hubs (together with a Hub in the US \citep{cramerEvaluationIndividualEnsemble2021} and one in Germany and Poland \citep{bracherShorttermForecastingCOVID192021}) which have been systematically collecting, aggregating and evaluating forecasts of several COVID-19 targets created by different teams every week. Forecasts are made one to four weeks ahead into the future and follow a quantile-based format with a set of 22 quantiles plus the median ($0.01, 0.025, 0.05, ..., 0.5, ... 0.95, 0.975, 0.99$).

The forecasts used for the purpose of this illustration are forecasts submitted between March 8 2021 and October 18 2021 for reported cases and deaths from COVID-19. We filtered all forecasts submitted to the Hub to only include models which have submitted forecasts for both deaths and cases for 4 horizons in 32 locations on at least 16 forecast dates (see Figure \ref{fig:HUB-num-avail-models}). Where not otherwise stated, we report results for a two-week-ahead forecast horizon.

In addition to the WIS we use pairwise comparisons \citep{cramerEvaluationIndividualEnsemble2021} to evaluate the relative performance of models across countries in the presence of missingness. In a first step, score ratios are computed for all pairs of models by taking the set of overlapping forecasts between the two models and dividing the score of one model over the score achieved by the other model. The relative skill for a given model compared to others is then obtained by taking the geometric mean of all score ratios which involve that model. Low values are better, and the average model receives a relative skill score of 1.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{output/figures/HUB-mean-obs-location.png}
    \caption{Observations and scores across locations and forecast horizons. A: Average (across all time points) of observed cases and deaths for different locations. B: Corresponding boxplot (y-axis on log-scale) of all cases and deaths. C: Scores for two-week-ahead forecasts from the EuroCOVIDhub-ensemble (averaged across all forecast dates) for different locations, evaluated on the natural as well as the logarithmic scale. D: Corresponding boxplots of all individual scores for two-week-ahead predictions. E: Boxplots for the relative change of scores for the EuroCOVIDhub-ensemble across forecast horizons. For any given forecast date and location, forecasts were made for four different forecast horizons, resulting in four scores. All scores were divided by the score for forecast horizon one.}
    \label{fig:HUB-mean-locations}
\end{figure}
